---
author: Gaurav Khadka
title: Civil Engineer
format:
  classic-cv-pdf: default
cvfooter:
  #left: "mr.schochastics.net"
  #right: "github.com/schochastics"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Graduate Student at University of Nebraska-Lincoln
    right: Nebraska, United States
  - title: Field
    left: Construction Engineering and Management
    #right: mr.schochastics.net
  - title: Interests
    left: Public-Private Partnership, Construction Analytics
    #right: david@schochastics.net
execute:
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary

Hello! I am a Construction Engineering and Management graduate student with a strong academic record and commitment to excellence. I have served as both a Graduate Teaching Assistant and Graduate Research Assistant at the University of Nebraska–Lincoln, supporting teaching construction courses and conducting extensive research. I am currently doing assignment for the course STAT 850 where we are learning how to make our CV using Latex in RStudio.

# Experience



```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    
    "Graduate Teaching Assistant", "University of Nebraska-Lincoln", "Aug 2024 - Present",
    "Durham School of Architectural Engineering and Construction",
    c(
      "Assisted in teaching CONE 221, CNST 498, and CNST 420, grading assignments, answering student queries, and supporting classroom activities.",
      "Helped organize and manage seminars and guest lectures for CNST 993."
    ),
    
    "Graduate Research Assistant", "University of Nebraska-Lincoln", "May 2025 - Aug 2025",
    "Durham School of Architectural Engineering and Construction",
    c(
      "Analyzed 180+ Canadian P3 projects using advanced statistical methods to evaluate how financing, project features, and market conditions affect cost efficiency and Value for Money.",
      "Assessed project bundling impacts on private investment, contract cost, Value for Money, and procurement time."
    ),
    
    "Civil Engineer Intern", "East Engineering Solutions Pvt. Ltd.", "Jun 2023 - Sep 2023",
    "",
    c(
      "Facilitated the preparation of detailed drawings and specifications for construction projects.",
      "Assisted site supervisor in site visits and inspections."
    )
) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")

```




# Education




```{r}
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    
    "Master of Science in Construction Engineering and Management", 
    "University of Nebraska-Lincoln", 
    "Nebraska, USA", 
    "Aug 2023 - Present", 
    c(
      "Research focused on Public-Private Partnership (P3) project bundling, Value for Money (VfM), and procurement efficiency in Canadian infrastructure projects.",
      "Coursework includes Project Administration, Urban Transportation Planning, and Multiple Regression Analysis."
    ),
    
    "Bachelor's in Civil Engineering", 
    "Pulchowk Campus, Institute of Engineering, Tribhuvan University", 
    "Lalitpur, Nepal", 
    "Dec 2018 - Apr 2023", 
    c(
      "Thesis: Detailed Engineering Survey, Design and Cost Estimation of Chaling Road.",
      "Conducted a detailed total cost estimation for a 3 km road span, demonstrating proficiency in financial analysis and project budgeting."
    )
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")

```

